\section{Honors and Awards}
\cventry{\small June 2016}{Qualcomm Scholarship, }{}{issued by Qualcomm.}{}{Offered to Tsinghua undergraduates with exceptional research experiences (top 1\%).}
\cventry{\small June 2015}{\href{http://www.google.cn/intl/en/university/student/scholarship-recipients.html}{Google Excellence Scholarship}, }{}{issued by Google.}{}{This scholarship is offered to Chinese undergraduate and graduate students who possess remarkable academic achievements and project experiences. 58 students are selected nationwide (6 in Tsinghua University).}
\cventry{\small April 2015}{\href{http://www.comap-math.com/mcm/2015Certs/37075.pdf}{Outstanding Winner}, }{Interdisciplinary Contest in Modeling 2015.}{}{}{Highest award (9 out of 2317) of the contest. Published a paper which models organizational churn using Bayesian-inspired methods and network science. See \href{https://github.com/jiamings/icm2015}{\color{blue} github.com/jiamings/icm2015} for more details. }
% issued by the Consortium for Mathematics and Its Applications (COMAP).
\cventry{\small April 2015}{Third Prize, }{33rd Tsinghua Challenge Cup, }{issued by Tsinghua University.}{}{Our project implements fast, scalable video segmentation and classification which utilizes deep activation features. Please see \href{http://jiamings.github.io/projects/decaf-video}{\color{blue} jiamings.github.io/projects/decaf-video} for details.}
\cventry{\small October 2014}{Outstanding Undergraduate, }{}{issued by the China Computer Federation (CCF).}{}{Only 4 students in Tsinghua, and 100 in China are awarded each year. }{}
% Attended China National Computer Congress, where we received the award and had the pleasure to meet Alexander Wolf (President of the ACM) and Ivan Sutherland (Turing Award 1988).
%\cventry{\footnotesize September 2014}{Tsinghua-Hengda Scholarship}{}{issued by Evergrande Group}{}{}{}
\cventry{\small May 2014}{Spark Program for Technological Innovation, }{}{Tsinghua University.}{}{Among top 50/3000 students for achievements in scientific and technological innovations.}{}
\cventry{\footnotesize December 2013}{Zhong Shimo Scholarship, }{}{issued by Dept. of Computer Science and Technology.}{}{Highest scholarship in the CS Department for academic achievements, social activities, and charity work. (top 0.75\%)}{}
\cventry{\small July 2011}{Bronze Prize, National Olympiad in Informatics, }{issued by China Computer Federation (CCF).}{}{}{}
