\section{Research Experiences}
\cventry{\footnotesize Sept 2016 - }{\href{http://futuredata.stanford.edu/}{Future Data Systems Group}, }{Stanford University. }{}{Advisor: Prof. \peterbailis}{Efficient unsupervised learning of time-series for \href{http://macrobase.io}{MacroBase} (outlier detection) using deep generative models.}


\cventry{\footnotesize April 2016 - July 2016}{Detection, Tracking and Reidentification Group, }{Megvii Inc. }{}{Mentor: Chi Zhang}{Developed a scalable framework to provide supervision for unlabeled data with trained models, which allows model distillation and merging network structures for different tasks, such as detection and parsing. \href{www.megvii.com}{\color{nblue} Megvii Inc.} is a leading unicorn start-up in China, with emphasis on machine learning and computer vision.}

%\cventry{\footnotesize December 2015 till now}{Lab of Multimedia, }{Tsinghua University. }{}{Advisors: Prof. \wenwuzhu  \& \pengcui.}{Inferenece of latent features in a social network.}

\cventry{\footnotesize July 2015 - September 2015}{Information Initiative @ Duke (iiD), }{Duke University. }{}{Advisor: Prof. \larrycarin .}{Worked on conditional factored deep generative models using recent Neural Variational Inference methods, which allows for semi-supervised deep learning and sequence generation with side information. \textbf{Our work is accepted by \textit{the 33rd International Conference on Machine Learning}.}}{}

\cventry{\footnotesize November 2014 - June 2015}{ Statistical AI \& Learning (TSAIL) Group, }{Tsinghua University. }{}{ Advisor: Prof. \junzhu .}{Explored stochastic variational methods for link prediction problems. Proposed an efficient method that would train on a network with over 3 million nodes, a significant improvement over original methods. \textbf{Our work is under review by \textit{the IEEE Transactions on Pattern Analysis and Machine Intelligence}. }}{}

\cventry{\footnotesize July 2014 - October 2014}{Visual Computing Group, }{Microsoft Research Asia. }{}{Advisor: \href{http://research.microsoft.com/en-us/um/people/jingdw/}{\color{nblue} Jingdong Wang}.}{Implemented a convolutional neural network for multiple label image annotation with \href{caffe.berkeleyvision.org}{\color{nblue} Caffe}.}{}%, which achieved state-of-the-art precision results.}{}
% Worked on classification and detection algorithms using deep learning methods; studied and modified Caffe, an open-source deep learning framework in C++ and CUDA; i

\cventry{\footnotesize October 2013 - June 2014}{TSAIL, }{Tsinghua University. }{}{Advisor: Prof. \junzhu .}{ Implemented a Gibbs sampling algorithm for \href{http://papers.nips.cc/paper/4981-scalable-inference-for-logistic-normal-topic-models.pdf}{\color{nblue} Scalable Inference for Logistic Normal Topic Models} (NIPS 2013).}{}